\documentclass[10pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\author{Abraham Toriz Cruz}
\title{Implementation of Map-Matching}
\begin{document}

\maketitle

\begin{abstract}
Para los que conocemos la ciudad de xalapa, usar el transporte público es una cuestión de haber experimentado algunas rutas durante nuestra vida. Para los que vienen de fuera es otra historia: no existe información completa sobre las líneas.

Para resolver esto entre 2016 y 2017 una comunidad llamada codeando xalapa organizó con ayuda del municipio un mapatón en el cual los usuarios del transporte público subían a los camiones con una aplicación y generaban trazas de GPS de los lugares por los que había pasado. Sin embargo esta información tiene errores asociados al error del GPS en la variedad de dispositivos usados para el rastreo.

En esta plática se hablará de la construcción de un problema de optimización a partir de la idea de obtener las calles por las que realmente pasó el autobús, dada la traza de GPS. Se abordarán las ideas actuales y distintas propuestas de cómo conectar un problema de la ciudadanía xalapeña con un modelo matemático que permita obtener el resultado esperado.
\end{abstract}

\begin{section}{Algorithm}

From the article.

\begin{enumerate}
	\item For each GPS position $z_i$, a set of candidate roads $\{r_i^0, r_i^1, \dots, r_i^n\}$ is determined, i.e. a set of all roads within a certain search-radius, for example 200m, around $z_i$.

	\item For each candidate road $r_i^j$, a \emph{measurement probability} is calculated which reflects how likely it is for a vehicle on road $r_i^j$ to emit a GPS measurement having position $z_i$. The probability depends on GPS error characteristics and decreases with increasing distance between road and GPS position.

	\item For each candidate road $r_i^j$ of a GPS position $z_i$, the \emph{transition probability} to all candidate roads $\{r_{i+1}^0, r_{i+1}^1, \dots, r_{i+1}^m\}$ of the next GPS position $z_{i+1}$ is calculated. The transition probability is an exponential function of the difference between the route length and the great circle distance between $z_i$ and $z_{i+1}$. The transition probability calculation therefore requires a shortest path routing between each pair of candidate roads, which is a computationally expensive operation.

	\item The Viterbi dynamic programming algorithm is applied to determine the map-matching solution by selecting the sequence of candidate roads which yields the overall best explanation for the observed GPS trajectory.
\end{enumerate}

\end{section}

\begin{section}{Important things to consider}
\begin{enumerate}
	\item Currently my approach is to use OSM street data, so the search graph is built by the nodes and not by lines. The search of roads within a radius is performed accordingly.
	\item The search radius will say how many routes per GPS position you have, thus changing the search graph size.
	\item For the test route a radius of $100m$ gives a minimum of one graph node and a maximum of 97, $150m$ give a minimum of 3 and maximum of 149, and $200m$ a minimum of 16 and a maximum of 236 nodes.
	\item You want the solution node to be within the search radius, but a large radius will make the search graph too big.
\end{enumerate}
\end{section}

\begin{section}{Tecnology}

\begin{enumerate}
	\item the Python programming language.

	\item Redis database. Two main groups of data stored:
	\begin{itemize}
		\item \textbf{base}. Data that does not change between computations, like the street graph or lua scripts.
		\item \textbf{track}. Data related to the current track being analized.
	\end{itemize}
\end{enumerate}

\end{section}

\end{document}
